---
title: "Christopher j. Lortie"
author: Progress report
header-includes:
  \renewcommand{\contentsname}{}
output:
  pdf_document:
    fig_caption: no
    toc: FALSE
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


### The relative importance of diversity at scale for direct restoration in drylands.
Several ongoing research topics needed to be addressed in the last 6 months. However, I am keen to now move forward and examine the relevance of diversity of plants and animals at different scales relevant to direct restoration efforts.  

### List of achievements  
```{r summary, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
summary <- read_csv("data/sample_summary.csv")
knitr::kable(summary) %>%
  column_spec(1, width = "1cm") %>%
  column_spec(2:3, width = "4cm") %>%
kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\newpage
### Proposed goals
1. Plan sampling at least two sites in California at different scales.  
2. Support floral diversity sampling for two projects.    
3. Write up Cuyama Micronet paper.  
4. Get RestoreNet setup.  
5. Complete RDM paper.  
6.  Complete step 1 of invert synthesis.  
7. Do meta on tipping points.  
8. Do meta on ecotypes.  

### Key questions  
1. How late is too late to set up Restorenet?
2. When is the best time to sample for diversity at scale?  
3. What is a good simple, back-up sampling project for diversity and restoration?   
4. How to time invert synthesis?  
5. When to fit in RDM paper?  

### Chapter updates
State details on 1-2 chapters that you seek input.